Gravitational field calculation in spherical coordinates using variable densities in depth

### 2018-11-12 manuscript/manuscript.tex
Fix minor spelling error

\noindent $f(r', \phi', \lambda')$ are the non-density dependent portion of the
integration kernels, $(r_i, \phi_j, \lambda_k)$ are the quadrature nodes, and $W_i^r$
are
the quadrature weights.

>>>>

\noindent $f(r', \phi', \lambda')$ is the non-density dependent portion of the
integration kernels, $(r_i, \phi_j, \lambda_k)$ are the quadrature nodes, and
$W_i^r$, $W_j^\phi$, $W_k^\lambda$ are the quadrature weights.
